---
title: "Churn"
output: html_document
date: "2024-12-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/User/OneDrive/Desktop/DSTI/SA Assignment")
health_data <- read.csv("cancer.csv")
head(health_data)
```
```{r}
str(health_data)
```

```{r}

health_data$ph.ecog <- as.factor(health_data$ph.ecog)
health_data$sex <- as.factor(health_data$sex)
str(health_data$status)
```


```{r}
# Display distinct values in the column
nrow(health_data)

# Check for missing values in each column
colSums(is.na(health_data))

library(naniar)

vis_miss(health_data)  # Heatmap of missing values


```

```{r}

# Recode 'status' to 0 and 1
health_data$status <- ifelse(health_data$status == 2, 1, 0)

```

install.packages("survival")
install.packages("survminer")
install.packages("devtools")
library(devtools)
devtools::install_github("modelplot/modelplotr")

install.packages("epiDisplay")


```{r}
library("survival")
library("survminer")
library("modelplotr")
```



```{r}
summary(health_data)
```



`

```{r}
# Fit the GLM model (logistic regression)
glm_model <- glm(status ~ ., family = binomial, data = health_data)

# Summarize the model
summary(glm_model)

```
# Nonparametric Estimation (Kaplan-Meier):

Suitable for survival function estimation.

```{r}
# Create survival object
surv_object = Surv(health_data$time, health_data$status)

km_fit <- survfit( surv_object ~ 1,data=health_data)

plot(km_fit, col = "blue", xlab = "Time", ylab = "Survival Probability",
     main = "Kaplan-Meier Survival Curve")
```

The survival probability drops below 20%, meaning most individuals have experienced the event ( death)


```{r}
km_sex_fit <- survfit( surv_object ~ sex, data=health_data)

plot(km_sex_fit, col = c("blue", "red"), xlab = "Time", ylab = "Survival Probability",
     main = "Kaplan-Meier Survival Curves by Sex")
legend("bottomleft", legend = c("Male", "Female"), col = c("blue", "red"), lty = 1)

```


Over the time , The survival probability for females (red) is higher than for males at most points in time.
This suggests that females tend to survive longer than males in the dataset.


```{r}
# List of variables to analyze (you can exclude unnecessary ones)
variables <- c("age", "ph.ecog", "ph.karno", "pat.karno")

# Perform Kaplan-Meier for each variable
for (var in variables) {
  # Fit Kaplan-Meier model
  formula <- as.formula(paste("surv_object ~", var))
  km_fit <- survfit(formula, data = health_data)
  
  # Plot the Kaplan-Meier survival curves
  plot(km_fit, col = rainbow(length(km_fit$strata)),
       xlab = "Time", ylab = "Survival Probability",
       main = paste("Kaplan-Meier Survival Curves by", var))
  
  legend("bottomleft", legend = names(km_fit$strata),
         col = rainbow(length(km_fit$strata)), lty = 1)
}

```




# Nonparametric Comparison (Log-Rank): 

Tests for differences between survival distributions.

```{r}
log_rank = survdiff(Surv(time, status) ~ sex, rho=0, data=health_data)

print(log_rank)
```
A p-value below 0.05 indicates that the difference in survival between the groups is statistically significant





# Semi-Parametric Model - Cox Regression: 

Evaluates covariates' effects while assuming proportional hazard

```{r}
cox = coxph(Surv(time, status) ~ sex, data=health_data)
summary(cox)
```




```{r}
# Fit a Cox Proportional Hazards model
cox_model <- coxph(Surv(time, status) ~ age + sex, data = health_data)

# Summary of the Cox model
summary(cox_model)

# Visualize the Cox model results (Hazard Ratios)
plot(cox.zph(cox_model))  # Test proportional hazards assumption

```




```{r}


```




```{r}
```




```{r}
```





```{r}
```





```{r}
```






```{r}
```





```{r}
```






```{r}
```





```{r}
```





```{r}
```





```{r}
```





```{r}
```



```{r}
```



```{r}
```



```{r}
```



```{r}
```




```{r}
```



```{r}
```



```{r}
```



```{r}
```



```{r}
```



```{r}
```




```{r}
```



```{r}
```



```{r}
```




```{r}
```




```{r}
```



```{r}
cox = coxph()
```




```{r}
```




```{r}
```




```{r}
```


